Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-22 wpe.tex
fix up haven paragraph

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify how much better one can predict the exact
state of a system from a distribution over system states evolved from 
a small ensemble around a prior known exact state, versus its asymptotic
distribution, requiring a model to perform the evolution. Our work
quantifies the predictability of a single observed time series using
weighted permutation entropy and makes no assumptions about the
underlying dynamics.

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven {\sl et al.} utilize the
relative entropy to quantify the difference in predictability between 
two distributions: one using the known dynamical system from a small 
ensamble in the past, and the other the asymptotic distribution. Our 
work quantifies the predictability of a single observed time series 
using weighted permutation entropy and makes no assumptions about the
generating process.
